---
title: "Xbox TrueAchievements Analysis"
output:
  html_document:
    theme: readable
    toc: true
    toc_depth: 3
    toc_float: true
    self_contained: true
    output_file: XboxTA_Analysis.html
---

[Home](../index.html)

[Analysis](./XboxTA_Analysis.html)

[Webscraping Methodology](./XboxTA_Webscrape.html)

[Exploratory Data Analysis](./XboxTA_EDA.html)

# Introduction:

The goal of this project is to analyze time series collections of achievement histories of a sample of gamers on Xbox's TrueAchievements website. Using this we can answer questions such as whether we can forecast engagement. 

## Data Details:

Data scraped from Xbox TrueAchievements using Python with NumPy, Pandas and Selenium. Details included with full report about the methodology.

[Webscraping Methodology](./XboxTA_Webscrape.html)

# Setup and Read Data

```{r Setup, include=FALSE}
set.seed(196)
library(tidyverse)
library(tidymodels)
library(lubridate)
library(forecast)
library(shiny)
library(plotly)
library(xgboost)
library(data.table)
library(caret)
library(stats)

source("./src/r/file.R")
source("./src/r/plots/plots.R")
source("./src/r/transformations/feature_transformations.R")
source("./src/r/variables/variables.R")
source("./src/r/models/models.R")
source("./src/r/models/ts_decomp.R")
```

## Create Files Directory

Here we get the file directories of all CSVs from the different gamer profiles to pull for analysis. This then applies transformations to keep a consistent format of dates of when the files were last scraped. 

```{r Create Files Directory}
directory_df = create_file_directory()
directory_df = directory_transformations(directory_df)
```

## Read Manifests

The full leaderboard of TA for future scraping outside of analysis and exploratory data analysis is loaded as well as the full manifest of achievements from the sample of profiles scraped thus far.

```{r Read Manifests}
lb_df = read.csv("./data/leaderboard/leaderboard.csv")
lb_df = lb_feature_transformations(lb_df)
achievements_manifest = read.csv("./data/manifest/achievements_manifest.csv")
```

## Read Sample of Gamers

A sample of 200 profiles using our file directory is taken and ordered by their anonymized IDs, generated from their orignial gamertags. 

```{r Sample Random Gamers}
set.seed(196)
rnd_gamer_sample = sample_random_gamers(200, directory_df = directory_df)
rnd_gamer_sample = lapply(rnd_gamer_sample, function(x) x[order(rnd_gamer_sample[[3]])])
```

# Transformations

## Achievement Transformations

Character type entries for when an achievement is earned are removed and replace with calculations of when the data was scraped. Currently two possibilities exist in "Today" and "Yesterday". Dates are formatted to one format and columns are added for month, day of the year and isoweek. A column tracking weekend / weekday is added here. 

```{r Achievements Transformations}
rnd_gamer_sample[[1]] = achievement_transform_today(rnd_gamer_sample[[1]], directory_df)
rnd_gamer_sample[[1]] = achievement_transform_yesterday(rnd_gamer_sample[[1]], directory_df)
rnd_gamer_sample[[1]] = achievement_transform_drop_offline(rnd_gamer_sample[[1]])
rnd_gamer_sample[[1]] = achievement_transform_format_dates(rnd_gamer_sample[[1]])
rnd_gamer_sample[[1]] = achievement_transform_extract_dates(rnd_gamer_sample[[1]])
```

## Game Transformations

Entries with unattainable values are removed. Currently, one title in "Defiance 2050" consistently shows absurdly high hours. Hours and minutes are split into different columns for both video games and apps. This is help remove the possiblity of hours from app time bloating a single profile.

```{r Game Transformations}
rnd_gamer_sample[[2]] = games_transform_drop_bad_titles(rnd_gamer_sample[[2]])
rnd_gamer_sample[[2]] = games_transform_hours(rnd_gamer_sample[[2]])
```

## Metrics Preprocessing (Total)

We output the total observations across all the sampled profiles to the screen. We then process through those profiles to generate a data frame of metrics akin to summary statistics.

```{r Metrics Preprocessing (Total Metrics)}
print(paste("TOTAL OBSERVATIONS:", get_total_observations(rnd_gamer_sample[[1]])))
metrics_df = process_metrics_df(rnd_gamer_sample, directory_df)
```

## Frequency Data Preprocessing

This intermediate step analyzes each profile in the sample by getting the frequency of achievements earned for every day. Note that this step does not include days in which no achievements were earned. 

```{r Metrics Preprocessing (Frequency Data)}
frequency_dfs = achievement_calculate_frequencies(rnd_gamer_sample)
frequency_combined_df = bind_rows(frequency_dfs, .id = "data_frame_id")
frequency_combined_df$data_frame_id = as.numeric(frequency_combined_df$data_frame_id)
```

## Daily Achievements Preprocessing

First we create a daily time series profile for each gamer for every day from when their first achievement is earned to when the data was last scraped. From here we can calculate churn and the variations of the EIR (Engagement Intensity Ratio) for the different profiles. These variations include the daily lifetime, weekly and monthly EIR. For these calculations, an additional column tracking how many days the profile has existed is implemented. 

```{r Metrics Preprocessing (Daily Achievements)}
da_df = calculate_daily_achievements(frequency_combined_df)
da_df = da_fill_dates(da_df)

da_profiles = da_split_by_profile(da_df)
da_profiles = da_profiles_set_churn(da_profiles)
da_profiles = da_profiles_set_days_existence(da_profiles)
da_profiles = calculate_daily_lt_eir(da_profiles)
da_profiles = calculate_weekly_eir_all(da_profiles)
da_profiles = calculate_monthly_eir_all(da_profiles)
```

# Time Series Analysis

## Time Series Decomposition

We iterate over the profiles and perform time series analysis on each profile, including sorting the data, creating time series objects, and applying decompositions. If a profile has insufficient data (less than two years), the decomposition step is skipped, and the profile is not included in the final result. The code returns a list of profiles, where each profile includes the original data frame, the time series objects, and the decompositions (if applicable). Skipped profiles are NULL.

```{r RQ1 : Time Series Decomposition}
ts_profiles = da_profiles_ts_decomp(da_profiles)
```

## Interactive Plot

This Shiny application allows users to explore time series decomposition plots for the different profiles in the sample. Users can select a profile to view their plots representing the implementations of EIR. It generates four plots using representing the original time series, trend, seasonal component, and residual component for each selected profile.

**Note:** This Shiny app won't display in the self-contained HTML file. To interact with the app, you can run the RMD document in an R Markdown viewer or in the RStudio IDE.

```{r RQ1 : Time Series Decomposition Plots Shiny}
generate_ts_shiny_plots(ts_profiles)
```

# Model Preparation

We prepare our models for evaluation by first removing any NULL data before analysis. Lists containing the indices for the training and testing sets for each of the target variables are made. For each of the target variables, lagged version are coded in at one day, 7 days, 14 days and 28 days. Observations with missing values are omitted so the first date of data analyzed is 28 days after the first achievement is earned. 

```{r RQ1 : Model Preparation (Remove NULL Data)}
ts_profiles = ts_profiles %>% keep(~ !is.null(.))
```

```{r RQ1 : Model Preparation (Daily LT EIR Target)}
daily_ltEIR_data = prepare_models(ts_profiles, "daily_lt_eir")
```

```{r RQ1 : Model Preparation (Days Since Last Achievement Target)}
days_since_achievement_data = prepare_models(ts_profiles, "days_since_achievement")
```

The first hyperparameter we are analyzing is the Time Series cross-validated folds created to evaluate model performance at 5, 10, 25 folds. These folds represent a fraction of the parameter passed tested on the next available fraction of the data available. For instance the CV folds at 5 will test the first 1/5th against the second 1/5th, the first 2/5ths against the 3/5th and so on until the last 1/5th is validated against the previous data up to that point. 

```{r RQ1 : Cross Validation Create Folds (Daily LT EIR Target)}
daily_ltEIR_5fold_full = get_cv_folds(daily_ltEIR_data$data_list, 5)
daily_ltEIR_10fold_full = get_cv_folds(daily_ltEIR_data$data_list, 10)
daily_ltEIR_25fold_full = get_cv_folds(daily_ltEIR_data$data_list, 25)

# Assuming you have an xgb.DMatrix called "dtrain"
daily_ltEIR_params <- list(
  objective = "reg:squarederror",
  eval_metric = "rmse",
  max_depth = 8,
  eta = 0.1,
  subsample = 0.8,
  colsample_bytree = 0.8
)
```

The second hyperparameter we observe is the number of boosting rounds in the XGBoost algorithm tested at 100 and 1000. An individual model is created using both 100 and 1000 boost rounds with 5, 10 and 25 folds cross folds for the target 1 variable. 

# Model Training

## Training (100 Rounds)

```{r RQ1 : Model Train 5 Fold, 100 Rounds, eval=FALSE}
daily_ltEIR_5fold_100n_models = lapply(1:length(daily_ltEIR_data$data_list), function(index) train_cv_target1_models(index, daily_ltEIR_5fold_full, daily_ltEIR_params, daily_ltEIR_data$data_list, daily_ltEIR_data$dtrain_list, 100))
```

```{r RQ1 : Model Train 10 Fold, 100 Rounds, eval=FALSE}
daily_ltEIR_10fold_100n_models = lapply(1:length(daily_ltEIR_data$data_list), function(index) train_cv_target1_models(index, daily_ltEIR_10fold_full, daily_ltEIR_params, daily_ltEIR_data$data_list, daily_ltEIR_data$dtrain_list, 100))
```

```{r RQ1 : Model Train 25 Fold, 100 Rounds, eval=FALSE}
daily_ltEIR_25fold_100n_models = lapply(1:length(daily_ltEIR_data$data_list), function(index) train_cv_target1_models(index, daily_ltEIR_25fold_full, daily_ltEIR_params, daily_ltEIR_data$data_list, daily_ltEIR_data$dtrain_list, 100))
```

## Performance Metrics (100 Rounds)

This interactive plot compares some performance metrics across the different number of folds at 100 rounds. These models were trained to predict daily lifetime EIR for each of the different profiles. The user selects which profile the model was trained on and compares performance metrics RMSE, MAPE, and SMAPE across the folds. For most profiles, the metrics trend downward (less error) with increasing folds and further in the folds. 

```{r RQ1 : Performance Metrics Shiny, 100 Rounds, eval=FALSE}
# UI
ui <- fluidPage(
  titlePanel("Evaluation Metrics"),
  sidebarLayout(
    sidebarPanel(
      selectInput("profile", "Select Profile:", choices = c(1:189))
    ),
    mainPanel(
      plotOutput("daily_ltEIR_5fold_100n_metrics_plot"),
      plotOutput("daily_ltEIR_10fold_100n_metrics_plot"),
      plotOutput("daily_ltEIR_25fold_100n_metrics_plot"),
      tableOutput("mean_metrics")
    )
  )
)

# Server
server <- function(input, output, session) {
  output$daily_ltEIR_5fold_100n_metrics_plot <- renderPlot({
    profile <- as.integer(input$profile)
    # Create a data frame with the evaluation metrics for the selected profile
    daily_ltEIR_5fold_100n_metrics_df <- data.frame(
      Fold = 1:length(daily_ltEIR_5fold_100n_models[[profile]][[3]][[1]]),
      RMSE = daily_ltEIR_5fold_100n_models[[profile]][[3]][[1]],
      MAPE = daily_ltEIR_5fold_100n_models[[profile]][[3]][[2]],
      SMAPE = daily_ltEIR_5fold_100n_models[[profile]][[3]][[3]]
    )
    # Plot the evaluation metrics
    ggplot(daily_ltEIR_5fold_100n_metrics_df, aes(x = Fold)) +
      geom_line(aes(y = RMSE, color = "RMSE"), size = 1) +
      geom_line(aes(y = MAPE, color = "MAPE"), size = 1) +
      geom_line(aes(y = SMAPE, color = "SMAPE"), size = 1) +
      labs(title = paste("Evaluation Metrics (5 Fold) - Profile", profile),
           x = "Fold",
           y = "Value",
           color = "Metric") +
      scale_color_manual(values = c("RMSE" = "red", "MAPE" = "blue", "SMAPE" = "green")) +
      theme_minimal()
  })
  output$daily_ltEIR_10fold_100n_metrics_plot <- renderPlot({
    profile <- as.integer(input$profile)
    # Create a data frame with the evaluation metrics for the selected profile
    daily_ltEIR_10fold_100n_metrics_df <- data.frame(
      Fold = 1:length(daily_ltEIR_10fold_100n_models[[profile]][[3]][[1]]),
      RMSE = daily_ltEIR_10fold_100n_models[[profile]][[3]][[1]],
      MAPE = daily_ltEIR_10fold_100n_models[[profile]][[3]][[2]],
      SMAPE = daily_ltEIR_10fold_100n_models[[profile]][[3]][[3]]
    )
    # Plot the evaluation metrics
    ggplot(daily_ltEIR_10fold_100n_metrics_df, aes(x = Fold)) +
      geom_line(aes(y = RMSE, color = "RMSE"), size = 1) +
      geom_line(aes(y = MAPE, color = "MAPE"), size = 1) +
      geom_line(aes(y = SMAPE, color = "SMAPE"), size = 1) +
      labs(title = paste("Evaluation Metrics (10 Fold) - Profile", profile),
           x = "Fold",
           y = "Value",
           color = "Metric") +
      scale_color_manual(values = c("RMSE" = "red", "MAPE" = "blue", "SMAPE" = "green")) +
      theme_minimal()
  })
  output$daily_ltEIR_25fold_100n_metrics_plot <- renderPlot({
    profile <- as.integer(input$profile)
    # Create a data frame with the evaluation metrics for the selected profile
    daily_ltEIR_25fold_100n_metrics_df <- data.frame(
      Fold = 1:length(daily_ltEIR_25fold_100n_models[[profile]][[3]][[1]]),
      RMSE = daily_ltEIR_25fold_100n_models[[profile]][[3]][[1]],
      MAPE = daily_ltEIR_25fold_100n_models[[profile]][[3]][[2]],
      SMAPE = daily_ltEIR_25fold_100n_models[[profile]][[3]][[3]]
    )
    # Plot the evaluation metrics
    ggplot(daily_ltEIR_25fold_100n_metrics_df, aes(x = Fold)) +
      geom_line(aes(y = RMSE, color = "RMSE"), size = 1) +
      geom_line(aes(y = MAPE, color = "MAPE"), size = 1) +
      geom_line(aes(y = SMAPE, color = "SMAPE"), size = 1) +
      labs(title = paste("Evaluation Metrics (25 Fold) - Profile", profile),
           x = "Fold",
           y = "Value",
           color = "Metric") +
      scale_color_manual(values = c("RMSE" = "red", "MAPE" = "blue", "SMAPE" = "green")) +
      theme_minimal()
  })
  output$mean_metrics <- renderTable({
  profile <- as.integer(input$profile)
  
  # Create a data frame with the mean metrics for the selected profile
  mean_metrics_df <- data.frame(
    Metric = rep(c("Mean RMSE", "Mean MAPE", "Mean SMAPE"), times = 3),
    Value = c(
      daily_ltEIR_5fold_100n_models[[profile]][[4]],
      daily_ltEIR_5fold_100n_models[[profile]][[5]],
      daily_ltEIR_5fold_100n_models[[profile]][[6]],
      daily_ltEIR_10fold_100n_models[[profile]][[4]],
      daily_ltEIR_10fold_100n_models[[profile]][[5]],
      daily_ltEIR_10fold_100n_models[[profile]][[6]],
      daily_ltEIR_25fold_100n_models[[profile]][[4]],
      daily_ltEIR_25fold_100n_models[[profile]][[5]],
      daily_ltEIR_25fold_100n_models[[profile]][[6]]
    ),
    Fold = rep(c("5-fold", "10-fold", "25-fold"), each = 3)
  )
  
  mean_metrics_df
})

}

# Run the Shiny app
shinyApp(ui = ui, server = server)

```

## Training (1000 Rounds)

```{r RQ1 : Model Train 5 Fold, 1000 Rounds, eval=FALSE}
daily_ltEIR_5fold_1000n_models = lapply(1:length(daily_ltEIR_data$data_list), function(index) train_cv_target1_models(index, daily_ltEIR_5fold_full, daily_ltEIR_params, daily_ltEIRdata$data_list, daily_ltEIRdata$dtrain_list, 1000))
```

```{r RQ1 : Model Train 10 Fold, 1000 Rounds, eval=FALSE}
daily_ltEIR_10fold_1000n_models = lapply(1:length(daily_ltEIR_data$data_list), function(index) train_cv_target1_models(index, daily_ltEIR_10fold_full, daily_ltEIR_params, daily_ltEIR_data$data_list, daily_ltEIRdata$dtrain_list, 1000))
```

```{r RQ1 : Model Train 25 Fold, 1000 Rounds, eval=FALSE}
daily_ltEIR_25fold_1000n_models = lapply(1:length(daily_ltEIR_data$data_list), function(index) train_cv_target1_models(index, daily_ltEIR_25fold_full, daily_ltEIR_params, daily_ltEIRdata$data_list, daily_ltEIRdata$dtrain_list, 1000))
```

## Performance Metrics (1000 Rounds)

This interactive plot compares some performance metrics across the different number of folds at 1000 rounds. These models were trained to predict daily lifetime EIR for each of the different profiles. The user selects which profile the model was trained on and compares performance metrics RMSE, MAPE, and SMAPE across the folds. For most profiles, the metrics trend downward (less error) with increasing folds and further in the folds. 

```{r RQ1 : Performance Metrics Shiny 1000n, eval = FALSE}
# UI
ui <- fluidPage(
  titlePanel("Evaluation Metrics"),
  sidebarLayout(
    sidebarPanel(
      selectInput("profile", "Select Profile:", choices = c(1:189))
    ),
    mainPanel(
      plotOutput("t1_5fold_1000n_metrics_plot"),
      plotOutput("t1_10fold_1000n_metrics_plot"),
      plotOutput("t1_25fold_1000n_metrics_plot"),
      tableOutput("mean_metrics")
    )
  )
)

# Server
server <- function(input, output, session) {
  output$t1_5fold_1000n_metrics_plot <- renderPlot({
    profile <- as.integer(input$profile)
    # Create a data frame with the evaluation metrics for the selected profile
    t1_5fold_1000n_metrics_df <- data.frame(
      Fold = 1:length(t1_5fold_1000n_models[[profile]][[3]][[1]]),
      RMSE = t1_5fold_1000n_models[[profile]][[3]][[1]],
      MAPE = t1_5fold_1000n_models[[profile]][[3]][[2]],
      SMAPE = t1_5fold_100n_models[[profile]][[3]][[3]]
    )
    # Plot the evaluation metrics
    ggplot(t1_5fold_1000n_metrics_df, aes(x = Fold)) +
      geom_line(aes(y = RMSE, color = "RMSE"), size = 1) +
      geom_line(aes(y = MAPE, color = "MAPE"), size = 1) +
      geom_line(aes(y = SMAPE, color = "SMAPE"), size = 1) +
      labs(title = paste("Evaluation Metrics - Profile", profile),
           x = "Fold",
           y = "Value",
           color = "Metric") +
      scale_color_manual(values = c("RMSE" = "red", "MAPE" = "blue", "SMAPE" = "green")) +
      theme_minimal()
  })
  output$t1_10fold_1000n_metrics_plot <- renderPlot({
    profile <- as.integer(input$profile)
    # Create a data frame with the evaluation metrics for the selected profile
    t1_10fold_1000n_metrics_df <- data.frame(
      Fold = 1:length(t1_10fold_1000n_models[[profile]][[3]][[1]]),
      RMSE = t1_10fold_1000n_models[[profile]][[3]][[1]],
      MAPE = t1_10fold_1000n_models[[profile]][[3]][[2]],
      SMAPE = t1_10fold_1000n_models[[profile]][[3]][[3]]
    )
    # Plot the evaluation metrics
    ggplot(t1_10fold_1000n_metrics_df, aes(x = Fold)) +
      geom_line(aes(y = RMSE, color = "RMSE"), size = 1) +
      geom_line(aes(y = MAPE, color = "MAPE"), size = 1) +
      geom_line(aes(y = SMAPE, color = "SMAPE"), size = 1) +
      labs(title = paste("Evaluation Metrics - Profile", profile),
           x = "Fold",
           y = "Value",
           color = "Metric") +
      scale_color_manual(values = c("RMSE" = "red", "MAPE" = "blue", "SMAPE" = "green")) +
      theme_minimal()
  })
  output$t1_25fold_1000n_metrics_plot <- renderPlot({
    profile <- as.integer(input$profile)
    # Create a data frame with the evaluation metrics for the selected profile
    t1_25fold_1000n_metrics_df <- data.frame(
      Fold = 1:length(t1_25fold_1000n_models[[profile]][[3]][[1]]),
      RMSE = t1_25fold_1000n_models[[profile]][[3]][[1]],
      MAPE = t1_25fold_1000n_models[[profile]][[3]][[2]],
      SMAPE = t1_25fold_1000n_models[[profile]][[3]][[3]]
    )
    # Plot the evaluation metrics
    ggplot(t1_25fold_1000n_metrics_df, aes(x = Fold)) +
      geom_line(aes(y = RMSE, color = "RMSE"), size = 1) +
      geom_line(aes(y = MAPE, color = "MAPE"), size = 1) +
      geom_line(aes(y = SMAPE, color = "SMAPE"), size = 1) +
      labs(title = paste("Evaluation Metrics - Profile", profile),
           x = "Fold",
           y = "Value",
           color = "Metric") +
      scale_color_manual(values = c("RMSE" = "red", "MAPE" = "blue", "SMAPE" = "green")) +
      theme_minimal()
  })
  output$mean_metrics <- renderTable({
    profile <- as.integer(input$profile)
    
    # Create a data frame with the mean metrics for the selected profile
    mean_metrics_df <- data.frame(
      Metric = c("Mean RMSE", "Mean RMSE", "Mean RMSE", "Mean MAPE", "Mean MAPE", "Mean MAPE", "Mean SMAPE", "Mean SMAPE", "Mean SMAPE"),
      Value = c(
        t1_5fold_1000n_models[[profile]][[4]],
        t1_10fold_1000n_models[[profile]][[4]],
        t1_25fold_1000n_models[[profile]][[4]],
        t1_5fold_1000n_models[[profile]][[5]],
        t1_10fold_1000n_models[[profile]][[5]],
        t1_25fold_1000n_models[[profile]][[5]],
        t1_5fold_1000n_models[[profile]][[6]],
        t1_10fold_1000n_models[[profile]][[6]],
        t1_25fold_1000n_models[[profile]][[6]]
      ),
      Fold = rep(c("5-fold", "10-fold", "25-fold"), each = 3)
    )
    
    mean_metrics_df
  })
}

# Run the Shiny app
shinyApp(ui = ui, server = server)

```
